DOM bridges and barriers: systematic review and survey

### 2025-12-08 reports/draft_results.qmd
update fig 6,7

#calc props for sankey_df csv (fine scale codes are raw totals from code_freq file)
sum_codes <- sum(code_freq$total) #710 codes
code_freq %>% 
  group_by(bridge_barr) %>% 
  summarise(totals = sum(total))

@@

#stacked bar plots
ggplot(freq_job_survey2, aes(fill=code_level, y=value, x=fish_ship)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","royalblue4","#45818E")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "") +
    guides(fill=guide_legend(nrow=2,byrow=TRUE))+
    theme_ms() +
    theme(legend.position = "top", 
          legend.justification = "left", 
          legend.text = element_text(size = 14, color = "black"))+
    xlab("") + 
    ylab("Proportion of theme (%)")

#ggsave("figures/ms_figs/industry/stack_survey.png", width = 7, height = 6, units = c("in"))
#ggsave("figures/slides_svg/stack_survey.svg", width = 7, height = 6, units = c("in"))

#radar plots
freq_job_survey3 <- freq_job_survey %>%
  # group_by(fish_ship, bridge_barr) %>%
  # mutate(n_total = sum(total)) %>%
  # ungroup() %>%
  # group_by(fish_ship, bridge_barr, code_name) %>%
  # mutate(n_subtotal = sum(total)) %>%
  # reframe(value = (n_subtotal/n_total)*100) %>%
  # ungroup() %>%
  #mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
  #distinct(id, .keep_all = TRUE) %>%
  #select(-c(id))
  group_by(fish_ship, bridge_barr, code_name) %>%
  summarise(value = sum(total))

@@

ggradar::ggradar(top_bridge,
        values.radar = c(0, 5, 10), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),#007172
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

@@

ggradar::ggradar(top_barrier,
        values.radar = c(0, 3, 6), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),#007172
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

#ggsave("figures/ms_figs/industry/radar_ba_survey.png", height = 8, width = 8, units = c("in"))
#ggsave("figures/slides_svg/radar_ba.svg", height = 8, width = 8, units = c("in"))

@@

table(n_job_lit$fish_ship)

>>>>

#calc props for sankey_df csv (fine scale codes are raw totals from code_freq file)
sum_codes <- sum(code_freq$total) #710 codes

code_freq %>% 
  group_by(bridge_barr) %>% 
  summarise(totals = sum(total))

@@

#stacked bar plots
freq_job_survey2$code_cat <- factor(freq_job_survey2$code_cat, levels = c("Data bridge", "Ecological bridge", "Social bridge", "Implementation bridge", "Data barrier", "Ecological barrier", "Social barrier", "Implementation barrier"))

ggplot(freq_job_survey2, aes(fill=code_cat, y=value, x=fish_ship)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#6D8C9E","#516875","#28343B", "#F1DA9F", "#FED240", "#DBA400", "#614900")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "") +
    guides(fill=guide_legend(nrow=2,byrow=TRUE))+
    theme_ms() +
    theme(legend.position = "top", 
          legend.justification = "left", 
          legend.text = element_text(size = 14, color = "black"))+
    xlab("") + 
    ylab("Percent of theme (%)")

#ggsave("figures/ms_figs/industry/stack_survey.png", width = 8, height = 6, units = c("in"))
#ggsave("figures/slides_svg/stack_survey.svg", width = 7, height = 6, units = c("in"))

#radar plots
freq_job_survey3 <- freq_job_survey %>%
  group_by(fish_ship, bridge_barr) %>%
  mutate(n_total = sum(total)) %>%
  ungroup() %>%
  group_by(fish_ship, bridge_barr, code_name) %>%
  mutate(n_subtotal = sum(total)) %>%
  reframe(value = (n_subtotal/n_total)*100) %>%
  ungroup() %>%
  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
  distinct(id, .keep_all = TRUE) %>%
  select(-c(id)) %>%
  group_by(fish_ship, bridge_barr, code_name) %>%
  summarise(value = sum(value))

@@

ggradar::ggradar(top_bridge,
        values.radar = c(0, 11, 22), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),#007172
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

@@

ggradar::ggradar(top_barrier,
        values.radar = c(0, 14, 28), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),#007172
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

ggsave("figures/ms_figs/industry/radar_ba_survey.png", height = 8, width = 8, units = c("in"))
#ggsave("figures/slides_svg/radar_ba.svg", height = 8, width = 8, units = c("in"))

@@

table(n_job_lit$fish_ship)
```
